\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For this reason, we mapped constraint types to \emph{DL} 
in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.

@@

%And since in every model there is only one, \emph{DL} sentences are satisfied. 

@@

%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
%(1) We mapped constraint types to \emph{DL} to logically underpin them and 
%(2) we described the constraint types' intended behavior in terms of validation results depending on CWA and UNA.
%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
%identical semantics of the languages with regard to the particular constraint type has to be ensured.
%%Constraint languages assume identical semantics, 
%%if for each constraint the following condition holds:
%If a constraint is represented by \emph{ShEx} and OWL 2, 
%the validation results must be exactly the same, i.e.,
%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
%We expressed constraint types by different languages
%to document identical semantics for these languages with regard to appropriate constraint types.

@@

\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%). Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types. On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.

\textbf{\emph{Complexity}:}
\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
%In case \emph{complex constraints} are expressible in \emph{DL}, 
%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Constraints of almost 14\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.

@@

Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets). We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
and \emph{simple constraints} may refer to a list of \emph{classes}.
The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} 
which may be an operator like $\sqsubseteq$.
\emph{Object Property Paths} (\emph{R-55})
ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
whose \emph{genre} is \emph{Popular-Science}, 
%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
and the property \emph{authorOfGenre} on the right side.
As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Object Property Paths as Property Constraint}
	\label{tab:property-constraint-object-property-paths}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}

There are \emph{simple constraints} which are not expressible in \emph{DL} but can still be described using the \emph{RDF-CV} 

@@

%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:

@@

how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in \emph{DL} and 
how the \emph{universal restriction} \emph{complex constraint} which is expressible in \emph{DL} are mapped to the \emph{RDF-CV}.

@@

%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}. 

@@

%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}. 
As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a title without an \emph{ISSN}, 
\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
The \emph{complex constraint} is generically expressible by \emph{DL}:
%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).

@@

%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
The \emph{DL} statements demonstrate that the \emph{complex constraint} 
is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).

@@

%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of \emph{DL}.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}).

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
\emph{DL} is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
When using \emph{keyfor} (\ms{isbn keyfor Book}), 
the \emph{complex constraint} can be formulated as a \emph{simple constraint} which looks like the following in concrete RDF turtle syntax:

@@

\emph{Complex constraints} of frequently used constraint types corresponding to \emph{DL} axioms like 
\emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
can also be simplified in the same way, 
as, although, such axioms can be expressed using basic \emph{DL} features, 
\emph{DL} axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
%Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
%It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL and the \emph{RDF-CV} as follows:
%
%\begin{DL}
%$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
%\end{DL}
%
%%\begin{gcotable}
%%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
%%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
%%\end{gcotable}
%
%\begin{table}
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
		%\end{tabular}
	%\caption{Primary Key Properties as Complex Constraints}
	%\label{tab:primary-key-properties-as-complex-constraints}
%\end{table}
%
%Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
%A key can be a datatype property, an object property, or a chain of properties.
%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
%This leads to the following DL and \emph{RDF-CV} mappings (only one \emph{simple property constraint}):
%
%\begin{DL}
%commandAuthorizationCode \ms{keyfor} StarfleetOfficer
%\end{DL}

@@

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
These constraint types form the basis to
lay the ground for discussions on validation
by defining a basic terminology and classification system for RDF constraints.
%
There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
%we mapped constraint types to \emph{DL} 
%to determine which \emph{DL} constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).

>>>>

The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For this reason, we mapped constraint types to DL 
in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.

@@

%And since in every model there is only one, DL sentences are satisfied. 

@@

%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
%(1) We mapped constraint types to DL to logically underpin them and 
%(2) we described the constraint types' intended behavior in terms of validation results depending on CWA and UNA.
%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
%identical semantics of the languages with regard to the particular constraint type has to be ensured.
%%Constraint languages assume identical semantics, 
%%if for each constraint the following condition holds:
%If a constraint is represented by \emph{ShEx} and OWL 2, 
%the validation results must be exactly the same, i.e.,
%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
%We expressed constraint types by different languages
%to document identical semantics for these languages with regard to appropriate constraint types.

@@

\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%). Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types. On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
%In case a constraint type is \emph{expressible in DL}, we determined which DL constructs are needed to express the constraint type.

\textbf{\emph{Complexity}:}
\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
%In case \emph{complex constraints} are expressible in DL, 
%DL statements representing \emph{complex constraints} contain DL statements standing for atomic and/or composed constraints. 
Constraints of almost 14\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.

@@

Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent DL constructs.

@@

%The \emph{constraining element} indicates the actual type of constraint like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in DL (e.g., regular expressions and constraining facets).

The \emph{constraining element} is an intuitive term which indicates the actual type of constraint. For the majority of the constraint types, there is exactly one constraining element. For the constraint type \emph{property domain (R-25, R-26)} which restricts the domain of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}. For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated for these constraint types. The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict given data properties to have a minimum, maximum, or exact number of relationships to literals with certain language tags. Thus, three constraining elements are needed in order to be able to express each possible constraint of that comstraint type.

If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$) and (in)equality (=, $\ne$). In case, constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely used terms from SPARQL and the DCMI Metadata Terms like \emph{regex} and \emph{xsd:pattern}. For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}. We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
and \emph{simple constraints} may refer to a list of \emph{classes}.
The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
the list of \emph{classes} includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.

For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} 
which may be a DL operator like $\sqsubseteq$.
\emph{Object Property Paths} (\emph{R-55})
ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the author of the book \emph{A-Brief-History-Of-Time} 
%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
whose genre is \emph{Popular-Science}, 
%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
the object property path {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an author of the genre \emph{Popular-Science}. 
%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
Thus, when representing the \emph{property constraint} using the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
and the property \emph{authorOfGenre} on its right side.
As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is set to the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Object Property Paths as Property Constraint}
	\label{tab:property-constraint-object-property-paths}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}

There are \emph{simple constraints} which are not expressible in DL but can still be described using the \emph{RDF-CV} 

@@

%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in DL, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:

@@

(1) how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in DL and 
(2) how the \emph{universal restriction} \emph{complex constraint} which is expressible in DL are represented using the \emph{RDF-CV}.

@@

%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in DL. 

@@

%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}. 
As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a title without an \emph{ISSN}, 
\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
The \emph{complex constraint} is generically expressible by DL:
%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by DL (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).

@@

%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in DL as follows:

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
The DL statements demonstrate that the \emph{complex constraint} 
is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).

@@

%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in DL - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of DL.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}).

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
DL is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
When using \emph{keyfor} (\ms{isbn keyfor Book}), 
the \emph{complex constraint} can be formulated as a \emph{simple constraint} which looks like the following in concrete RDF turtle syntax:

@@

\emph{Complex constraints} of frequently used constraint types corresponding to DL axioms like 
\emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
can also be simplified in the same way, 
as, although, such axioms can be expressed using basic DL features, 
DL axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
%Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
%It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL and the \emph{RDF-CV} as follows:
%
%\begin{DL}
%$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
%\end{DL}
%
%%\begin{gcotable}
%%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
%%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
%%\end{gcotable}
%
%\begin{table}
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
		%\end{tabular}
	%\caption{Primary Key Properties as Complex Constraints}
	%\label{tab:primary-key-properties-as-complex-constraints}
%\end{table}
%
%Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
%A key can be a datatype property, an object property, or a chain of properties.
%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
%This leads to the following DL and \emph{RDF-CV} mappings (only one \emph{simple property constraint}):
%
%\begin{DL}
%commandAuthorizationCode \ms{keyfor} StarfleetOfficer
%\end{DL}

@@

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
These constraint types form the basis to
lay the ground for discussions on validation
by defining a basic terminology and classification system for RDF constraints.
%
There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
%we mapped constraint types to DL 
%to determine which DL constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
